probKanren: A Simple Probabilistic extension for microKanren

### 2021-09-14 paper/main.tex
Use correct grammar in examples

\begin{minted}{Scheme}
  (run 1000 (q)
    (normal 0 3 q)
    (normal q 0 4))
\end{minted}

\begin{minted}{Scheme}
  (run 1000 (q)
    (beta 1 1 q)
    (bern q 1.0))
\end{minted}

@@

\textsc{microKanren}\cite{10.1145/2989225.2989230, daniel2018reasoned}
is a pure logic programming language embedded in Scheme. The language
consists of a set of terms, a set of goal primitives, and two run
functions to answer queries in the language. The goal primitives
consist of a \texttt{fresh} form for introducing logic variables, a
unification primitive, a conjunction combinator, a disjunction
combinator, and ways to define and use relations.

@@

<term-expr> ::= (quote <datum>) \alt
                <lexical-var-ref> \alt
                (cons <term-expr> <term-expr>)

@@

To create probkanren we extend this grammar with distribution clauses
such as \texttt{normal} and \texttt{flip}. These are just another type
of goal expression. We do not need to add a notion of probabilistic
variables as they can just be seen as logic variables constrained in
a particular way.

@@

>>>>

\begin{minted}{Scheme}
  (run 1000 (q)
   (conj
    (normal 0 3 q)
    (normal q 2 4))]
\end{minted}

%% \begin{minted}{Scheme}
%%   (run 1000 (q)
%%     (uniform 0 1 q)
%%     (bern q 1.0))
%% \end{minted}

@@

\textsc{microKanren}\cite{10.1145/2989225.2989230, daniel2018reasoned}
is a pure logic programming language embedded in Scheme. The language
consists of a set of terms, a set of goal primitives, and two run
functions to answer queries in the language. The goal primitives
consist of a \texttt{fresh} form for introducing logic variables, a
unification primitive \texttt{==}, a conjunction combinator \texttt{conj}, a disjunction
combinator \texttt{disj}, and ways to define and apply relations.

@@

<term-expr> ::= (quote <datum>) \alt
                <lexical-var-ref> \alt
                (cons <term-expr> <term-expr>) \alt
                <term>

@@

To create \textsc{probKanren} we extend this grammar with distribution clauses
such as \texttt{normal} and \texttt{bern}. These are just another type
of goal expression. We do not need to add a notion of probabilistic
variables as they can just be seen as logic variables constrained in
a particular way.

@@

\section{Semantics of probKanren}
